### 2016-09-16 Chapters/QuantumMechanics.tex
Only acknowledgements missing

To first order, one has:
\begin{equation}\label{eq:1st-order}
  \denom{\mu_2}\tamp{\mu_2}^{[1]}
  = - \braket{\mu_2 | \Phi | \mathrm{HF}}
  = - \braket{\mathrm{HF} | \commutator{\Phi}{\cluster{\mu_2}} |
  \mathrm{HF}}
  = \denom{\mu_2}\tbar{\mu_2}^{[1]}
\end{equation}
which shows that singles, due to Brillouin's condition, and triples
amplitudes are of second and higher order.
For second order singles, doubles and triples one obtains:
\begin{equation}\label{eq:2nd-order}
  \denom{\mu_q}\tamp{\mu_q}^{[2]}
  = - \braket{\mu_q | \commutator{\Phi}{T_2^{[1]}} | \mathrm{HF}}
  = - \braket{\tbar{2}^{[1]} | \commutator{\Phi}{\cluster{\mu_q}} |
  \mathrm{HF}}
  = \denom{\mu_q}\tbar{\mu_q}^{[2]}
\end{equation}
According to the $2n+1$ and $2n+2$ rules, energy corrections up to fifth
order can be obtained from amplitudes and multipliers up to second
order. Since the triples first appear to second order, the \gls{CCSD}
energy is correct to third order in the fluctuation potential.
The triples contributions to the fourth and fifth order corrections to
the energy are given as:
\begin{subequations}
  \begin{align}
    E_T^{[4]} &=
 \braket{\tbar{2}^{[1]}| \commutator{\Phi}{T_3^{[2]}} | \mathrm{HF}}
 \label{eq:4th-order-triples} \\
    E_T^{[5]} &=
    \braket{\tbar{1}^{[2]} | \commutator{\Phi}{T_3^{[2]}} | \mathrm{HF}}
  + \braket{\tbar{2}^{[2]} | \commutator{\Phi}{T_3^{[2]}} | \mathrm{HF}}
  \nonumber \\
  &+ \braket{\tbar{3}^{[2]} | \commutator{\Phi}{T_2^{[2]}} | \mathrm{HF}}
  + \braket{\tbar{3}^{[2]} | \commutator{\Phi}{T_3^{[2]}} | \mathrm{HF}}
  \nonumber \\
    &+
    \frac{1}{2}\braket{\tbar{3}^{[2]} |
    \commutator{\commutator{\Phi}{T_2^{[1]}}}{T_2^{[1]}}
    | \mathrm{HF}}.
 \label{eq:5th-order-triples}
  \end{align}
\end{subequations}
These expressions form the basis for the development of reduced-scaling
\acrshort*{CC} schemes were the double and triple excitation are treated
approximately. These are the subject of the next Section.

>>>>

To first order, one has:
\begin{equation}\label{eq:1st-order}
  \denom{\mu_2}\tamp{\mu_2}^{[1]}
  = - \braket{\mu_2 | \Phi | \mathrm{HF}}
  = - \braket{\mathrm{HF} | \commutator{\Phi}{\cluster{\mu_2}} |
  \mathrm{HF}}
  = \denom{\mu_2}\tbar{\mu_2}^{[1]}
\end{equation}
which shows that singles, due to Brillouin's condition, and triples
amplitudes are of second and higher order.
For second order singles, doubles and triples one obtains:
\begin{equation}\label{eq:2nd-order}
  \denom{\mu_q}\tamp{\mu_q}^{[2]}
  = - \braket{\mu_q | \commutator{\Phi}{T_2^{[1]}} | \mathrm{HF}}
  = - \braket{\tbar{2}^{[1]} | \commutator{\Phi}{\cluster{\mu_q}} |
  \mathrm{HF}}
  = \denom{\mu_q}\tbar{\mu_q}^{[2]}
\end{equation}
According to the $2n+1$ and $2n+2$ rules, energy corrections up to fifth
order can be obtained from amplitudes and multipliers up to second
order:
\begin{subequations}\label{eq:mbpt-energies}
  \begin{align}
    E^{[1]}
    &= \braket{\mathrm{HF} | \Phi | \mathrm{HF}} \label{eq:mbpt-1st} \\
    E^{[2]}
    &= \braket{\mathrm{HF} | \commutator{\Phi}{T_2^{[1]}} | \mathrm{HF}} \label{eq:mbpt-2nd} \\
    E^{[3]}
    &= \braket{\tbar{2}^{[1]} | \commutator{\Phi}{T_2^{[1]}} | \mathrm{HF}} \label{eq:mbpt-3rd} \\
    E^{[4]} &= \braket{\tbar{2}^{[1]} | \commutator{\Phi}{T^{[2]}} |
    \mathrm{HF} }
    +
    \braket{\tbar{2}^{[1]} | \BCHsecond{\Phi}{T_2^{[1]}}|
    \mathrm{HF} } \label{eq:mbpt-4th} \\
    E^{[5]} &=
    \braket{\mathrm{HF} | \BCHsecond{\Phi}{T^{[2]}}|\mathrm{HF} }
    + \braket{\tbar{2}^{[1]} |
    \commutator{\commutator{\Phi}{T^{[2]}}}{T_2^{[1]}}
    | \mathrm{HF} } \nonumber \\
    &+ \sum_{u=1}^\mathcal{M}
    \braket{\tbar{u}^{[2]} | \BCHfirst{\Phi}{T^{[2]}}|
    \mathrm{HF} }
    +\sum_{u=1}^\mathcal{M}
    \braket{\tbar{u}^{[2]} | \BCHsecond{\Phi}{T_2^{[1]}}|
    \mathrm{HF} } \label{eq:mbpt-5th}
  \end{align}
\end{subequations}

Since the triples first appear to second order, the \gls{CCSD}
energy is correct to third order in the fluctuation potential.
The triples contributions to the fourth and fifth order corrections to
the energy are given as:
\begin{subequations}
  \begin{align}
    E_T^{[4]} &=
 \braket{\tbar{2}^{[1]}| \commutator{\Phi}{T_3^{[2]}} | \mathrm{HF}}
 \label{eq:4th-order-triples} \\
    E_T^{[5]} &=
    \braket{\tbar{1}^{[2]} | \commutator{\Phi}{T_3^{[2]}} | \mathrm{HF}}
  + \braket{\tbar{2}^{[2]} | \commutator{\Phi}{T_3^{[2]}} | \mathrm{HF}}
  \nonumber \\
  &+ \braket{\tbar{3}^{[2]} | \commutator{\Phi}{T_2^{[2]}} | \mathrm{HF}}
  + \braket{\tbar{3}^{[2]} | \commutator{\Phi}{T_3^{[2]}} | \mathrm{HF}}
  \nonumber \\
    &+
    \frac{1}{2}\braket{\tbar{3}^{[2]} |
    \commutator{\commutator{\Phi}{T_2^{[1]}}}{T_2^{[1]}}
    | \mathrm{HF}}.
 \label{eq:5th-order-triples}
  \end{align}
\end{subequations}
These expressions form the basis for the development of reduced-scaling
\acrshort*{CC} schemes were the double and triple excitation are treated
approximately. These are the subject of the next Section.
